Endogenous Politics and the Design of Trade Institutions\thanks{I thank Kyle Bagwell, Mostafa Beshkar, Rick Bond, Chad Bown, Nuno Limao, Giovanni Maggi, Anson Soderbery, Bob Staiger, Maurizio Zanardi, Ben Zissimos and participants in seminars at SITE for very helpful comments and discussions.}

### 2024-08-08 draft.tex
comment out addbibresource lines that threw warnings
Add .bib file from my hard drive and recompile

%dell laptop
\addbibresource{C:/Users/Kristy/Dropbox/Research/xBibs/tradeagreements.bib}

%campus computer
\addbibresource{C:/Apps-SU/Dropbox/Research/xBibs/tradeagreements.bib}
\renewcommand{\newunitpunct}{,}
\renewbibmacro{in:}{}

@@

\vskip.3in
\begin{center} {\bf Abstract} \end{center}
\begin{quote}
{\small While most of the literature on the design of trade agreements and trading institutions takes the political pressure governments face to be exogenous, this paper endogenizes politics in a standard model for studying trade policy design questions. One can use this simple modeling framework to distinguish between the dynamics induced by exogenous political shocks and endogenous incentives of political actors, unifying these two strands of literature. The modeling framework can also provide fuller answers to trade policy design questions by elucidating the interactions between exogenous and endogenous political forces.  Applications to tariff caps and the escape clause show that important insights are missed if attention is restricted to exogenous political shocks. Most notably, endogenous politics destroys a traditionally-defined escape clause's ability to provide flexibility in the face of political shocks when lobbies use the flexibility to seek rents. This can explain why WTO Safeguard use is conditioned on measurable economic indicators.}
\end{quote}

>>>>

%dell laptop
%\addbibresource{C:/Users/Kristy/Dropbox/Research/xBibs/tradeagreements.bib}

%Surface Book 2
\addbibresource{tradeagreements.bib}

%campus computer
%\addbibresource{C:/Apps-SU/Dropbox/Research/xBibs/tradeagreements.bib}
\renewcommand{\newunitpunct}{,}
\renewbibmacro{in:}{}

@@

\vskip.3in
\begin{center} {\bf Abstract} \end{center}
\begin{quote}
{\small While most of the literature on the design of trade agreements and trading institutions takes the political pressure governments face to be exogenous, this paper endogenizes politics in a standard model for studying trade policy design questions. One can use this simple modeling framework to distinguish between the dynamics induced by exogenous political shocks and endogenous incentives of political actors, unifying these two strands of literature. The modeling framework can also provide fuller answers to trade policy design questions by clarifying the interactions between exogenous and endogenous political forces. Applications to tariff caps and the escape clause show that important insights are missed if attention is restricted to exogenous political shocks. Most notably, endogenous politics destroys a traditionally-defined escape clause's ability to provide flexibility in the face of political shocks when lobbies use the flexibility to seek rents. This can explain why WTO Safeguard use is conditioned on measurable economic indicators.}
\end{quote}
